### 2018-05-30 1_intro.tex
Add example on cfg in cfg to eval. Add two siks to summary.

All the tools listed above consider only a single memory model, however, in real life we face serious engineering problems involving more than one execution environment.
One of these problems is the \textit{portability analysis} of the program from one hardware architecture to another.
A program written in a high-level language is compiled for different hardware architectures.
Even if all the compiler optimisations were disabled (which is a rare case nowadays), the behaviour of two compiled versions of the same program may differ due to differences between hardware memory models.
As the result, a program compiled under the platform $\mathcal{T}$ can reach states that are unreachable on the platform $\mathcal{S}$, which is a \textit{portability bug} from the source platform $\mathcal{S}$ to the target platform $\mathcal{T}$~\cite{Porthos17a}.

>>>>

All the tools listed above consider only a single memory model, however, in real life we face serious engineering problems involving more than one execution environment.
One of these problems is the \textit{portability analysis} of the program from one hardware architecture to another.
A program written in a high-level language is compiled for different hardware architectures.
Even if all the compiler optimisations were disabled (which is a rare case nowadays), the behaviour of two compiled versions of the same program may differ due to differences between hardware memory models.
As the result, a program compiled for the platform $\mathcal{T}$ can reach states that are unreachable on the platform $\mathcal{S}$, which is a \textit{portability bug} from the source platform $\mathcal{S}$ to the target platform $\mathcal{T}$~\cite{Porthos17a}.

### 2018-05-30 4_impl.tex
Add example on cfg in cfg to eval. Add two siks to summary.

The general processing scheme of old tool \porthos[1] is the following.
The input program is parsed to the AST, where leaves are the events.
The instructions of the AST are then encoded into the $\phi_{CF}$ (see Section~\ref{ch:enc:bmc:cf}) and the events are processed by the single function (`\texttt{dartagnan.wmm.Domain.encode}') that loops over all events, checks their properties (the kind of event, the operands of the memory event, the type of the barrier event, etc.) and adds corresponding relations assertions to the formula.
Encoding all the relations (the \textit{program domain encoding}) in a single function is error-prone and hardly manageable.
Moreover, this function does not consider the memory model, therefore the result formula can contain relations that are not constrained by the memory model specified by the user and thus are redundant (for instance, the \texttt{TSO} memory model does not contain \texttt{POWER}-specific relations \texttt{ii}, \texttt{ic}, \texttt{ci}, etc., that are always encoded regardless the memory model).
In \porthos[2], we moved the encoding logic into a separate module (see Section~\ref{ch:impl:proc:z-encoder}) that accepts the input program and the user-defined memory model, therefore does not add constraints over unused relations to the result SMT-formula.

The high-level architecture of \porthos[2] is presented in Figure~\ref{fig:arch}.
The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models.
However, instead of parsing memory models from the \cat{} file, the tool may operate with pre-defined memory models (\texttt{SC}, \texttt{TSO}, \texttt{PSO}, \texttt{RMO}, \texttt{ALPHA}, \texttt{POWER}, \texttt{ARM}; this feature is inherited from \porthos[1]).
The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \ytree{}%
%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.}%
%
(Section~\ref{ch:impl:model:ytree}), which then is being preprocessed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \ytree{} then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \xgraph{} representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \xgraph{} then is being converted to an acyclic form (Section~\ref{ch:impl:proc:x-unroll}) in order to be encoded into a \zformula{} (Section~\ref{ch:impl:model:zformula}).
Apart from that, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the abstract syntax tree of derived relations of the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
%on the basis of the \xgraph{} in order to build the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \wmodel{} and acyclic \xgraph{} are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \zformula{} representation (a wrapper over an SMT-formula), which then is translated to an SMT-formula, which then is solved by the SMT-solver.
Although this general architecture is defined for

@@

According to the C standard, \textit{"any statement may be preceded by a prefix that declares an identifier as a label name"}.
The \ytree{} statements of follow this rule, however they these labels are symbolic, and they need to be resolved at the pre-compilation stage.
Apart from the set of statements listed before, we define the \texttt{YFunctionDefinition} and its inheritor a litmus-specific declaration \texttt{YProcessDefinition}
used in intra-procedural analysis mode.
The function definition contains the \texttt{YCompoundStatement} body and the \texttt{YMethodSignature} signature (method name and types of formal parameters), which is used in the function resolution during the pre-compilation stage.
The other litmus-specific statements are \texttt{YPreludeStatement}
that carries the list of \texttt{YStatement} initial writes, and \texttt{YPostludeStatement} 
that carries the \texttt{YExpression} binary expression to be asserted by the litmus test.

@@

@@

The label resolution is necessary for establishing links to labelled statements.
In C, labelled statements are declared via the colon-syntax `\texttt{<label>\;:\;<statement>}', and the labels are referenced by the jump-statement `\texttt{goto\;<label>}'.
The label resolution algorithm traverses the \ytree{} and collects all declared labels into a map that points a label to the labelled statement.
This information is used during compilation to set up unconditional jumps.

@@

The main class representing the X-compiler is \texttt{Y2XConverter}. %TODO: draw it in Figure.
It receives as input the \ytree{}, the memory model kind and user settings (for instance, the interpreter mode defining the set of invocation hooks enabled during the analysis run).
The \texttt{Y2XConverter} creates an instance of the stateless visitor \texttt{Y2XConverterVisitor} that traverses the \ytree{} while invoking the stateful interpreter \texttt{XInterpreter}.
The \texttt{XInterpreter} carries the \xgraph{}-builder and provides \textit{action} methods for changing its state and thus the filling in the builder.
The interpreter has additional modules \texttt{XMemoryManager}, \texttt{XHookManager} and \texttt{XTypeManager} that provide specialised functionality.

@@

The invocation hooking module serves as a knowledge base that stores the semantics of functions.
Once the X-compiler meets the function invocation, it calls the \texttt{XHookManager}, which tries to match the function signature (in the case of program in C language -- only the function name) across all signatures it stores.
If the signature matches, the hook manager intercepts the function call and interprets the hook action instead of invoking the function directly.
The hook manager enables only invocation hooks that are compliant with the language of the input program.
All invocation hooks implement the interface \texttt{XInvocationHook}.
The result of an invocation hook interception is the \texttt{XInvocationHookAction}, a delayed operation implemented on the top of lambda functions of Java.
The hook action is invoked with actual arguments and returns an arbitrary \texttt{XEntity} as the result of invocation.

@@

Once the graph is unrolled, it can be augmented by data-flow edges.
As it was discussed in Section~\ref{ch:impl:model:xgraph}, the data-flow edges can represent either \rf{}- or \co{}-relation.
The \rf{}-edges join each write event to all read events that access the same location; the \co{}-edges join write events to the same location.
Currently, \porthos[2] does not yet construct the \xgraph[DF] component of the full \xgraph{}, instead, it uses the function `\texttt{dartagnan.wmm.Domain.encode}' of \porthos[1] to encode data-flow relations and derived relations of the \xgraph[CF].

>>>>

The general processing scheme of the old tool \porthos[1] is the following.
The input program is parsed to the AST, where leaves are the events.
%The instructions of the AST are encoded into the $\phi_{CF}$ (see Section~\ref{ch:enc:bmc:cf})
The control-flow of the program is encoded into an SMT-formula as it was discussed in Section~\ref{ch:enc:bmc:cf}, and the data-flow (\po{}- and \rf{}- relations) and some derived relations are encoded by the single function (`\texttt{dartagnan.wmm.Domain.encode}') that loops over all events, checks their properties (the kind of event, the operands of the memory event, the control-flow properties such as condition level, etc.) and adds the assertions of corresponding relations to the formula.
Encoding all the relations (the \textit{program domain encoding}) in a single large function is an error-prone and hardly manageable approach.
Moreover, the events, that constitute the elements of a composite data structure, carry the information about it (such as the condition level, which is the property of the control-flow graph), while it should be carried by the data structure itself.
%This approach is highly extensible
In addition, the program domain encoding function does not consider the memory model, therefore the result formula can contain relations that are not constrained by the memory model specified by the user and thus are redundant (for instance, the \texttt{TSO} memory model does not contain \texttt{POWER}-specific relations \texttt{ii}, \texttt{ic}, \texttt{ci}, etc., that are always encoded regardless the memory model).
In \porthos[2], we moved the encoding logic into a separate module (see Section~\ref{ch:impl:proc:z-encoder}) that accepts the input program and the user-defined memory model, therefore does not add constraints over unused relations to the result SMT-formula.

The high-level architecture of \porthos[2] is presented in Figure~\ref{fig:arch}.
The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models.
However, instead of parsing memory models from the \cat{} file, the tool may operate with pre-defined memory models (\texttt{SC}, \texttt{TSO}, \texttt{PSO}, \texttt{RMO}, \texttt{ALPHA}, \texttt{POWER}, \texttt{ARM}; this feature is inherited from \porthos[1]).
The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \ytree{}%
%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.}%
%
(Section~\ref{ch:impl:model:ytree}), which then is being preprocessed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \ytree{} then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \xgraph{} representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \xgraph{} then is being converted to an acyclic form (Section~\ref{ch:impl:proc:x-unroll}) in order to be encoded into a \zformula{} (Section~\ref{ch:impl:model:zformula}).
Apart from that, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the abstract syntax tree of derived relations of the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
%on the basis of the \xgraph{} in order to build the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \wmodel{} and acyclic \xgraph{} are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \zformula{} representation (a wrapper over an SMT-formula), which then is translated to an SMT-formula, which then is solved by the SMT-solver (note, current implementation of \porthos[2] excludes the \zformula{} as at the moment it is enough for \porthos[2] to use only a single SMT-solver).

%Although the general architecture is designed to separate clearly the internal representations used by the program, we have not yet implemented several modules listed before.
%For instance, the \xgraph{} is constructed only partially, i.e., only the control-flow graph \xgraph[CF] is built during the program compilation.
%After this, the graph is unrolled and encoded directly into an SMT-formula, avoiding the \zformula{} abstraction layer as temporarily unnecessary.
%The data-flow analysis is performed on the stage of SMT-encoding with usage of the SSA-map (see Section~\ref{ch:enc:bmc:df}).
%Thus, the current implementation of \porthos[2] implies the \xgraphU[CF] to be passed to the program domain encoder of the old code base, which was discussed above.

@@

According to the C standard, \textit{"any statement may be preceded by a prefix that declares an identifier as a label name"}.
The \ytree{} statements of follow this rule, however they these labels are symbolic, and they need to be resolved at the pre-compilation stage.
Apart from the set of statements listed before, we define the \texttt{YFunctionDefinition} and its inheritor a litmus-specific definition \texttt{YProcessDefinition}
used in intra-procedural analysis mode.
The function definition contains the \texttt{YCompoundStatement} body and the \texttt{YMethodSignature} signature (method name and types of formal parameters), which is used in the function resolution during the pre-compilation stage.
The other litmus-specific definitions are \texttt{YPreludeDefinition}
that carries the list of \texttt{YStatement} initial writes, and \texttt{YPostludeDefinition} 
that carries the \texttt{YExpression} binary expression to be asserted by the litmus test.

@@

%TODO: check this %Note, as it was above, the data-flow componen \xgraph[DF] of the event-flow graph is not yet constructed

@@

The label resolution is necessary for establishing links to labelled statements.
In C, labelled statements are declared via the colon-syntax `\texttt{<label>\;:\;<statement>}', and the labels are referenced by the jump-statement `\texttt{goto\;<label>}'.
The label resolution algorithm traverses the \ytree{} and collects all declared labels into a map \texttt{JumpsResolver} that points a label to the labelled statement.
This information is used during compilation to set up unconditional jumps.

@@

The main class representing the X-compiler is \texttt{Y2XConverter}.
It receives as input the \ytree{}, the memory model kind and user settings (for instance, the interpreter mode defining the set of invocation hooks enabled during the analysis run).
The \texttt{Y2XConverter} creates an instance of the stateless visitor \texttt{Y2XConverterVisitor} that traverses the \ytree{} while invoking the stateful interpreter \texttt{XInterpreter}.
The \texttt{XInterpreter} carries the \xgraph{}-builder and provides \textit{action} methods for changing its state and thus the filling in the builder.
The interpreter has additional modules \texttt{XMemoryManager}, \texttt{XHookManager} and \texttt{XTypeManager} that provide specialised functionality.

@@

The invocation hooking module serves as a compiler knowledge base that stores the semantics of high-level functions in terms of low-level event-flow graph elements.
%Invocation hooks should be used for describing the 
For example, the C11 sequentially consistent load operation `\lstinline{l.store(memory_order_seq_cst, r)}' whould be compiled for the \texttt{x86} architecture as the write instruction `\lstinline{MOV l, r}' followed by the fence instruction `\lstinline{MFENCE}', whether for the \texttt{POWER} architecture this code would be compiled as the `\lstinline{hwsync}' followed by the store instruction.
This is called the \textit{compiler mapping}.
While the \xgraph{} is the abstract (hardware-agnostic) low-level program representation, the compiler mapping is the only component of the compiler that produces differences between two versions of the same program compiled for different architectures.

The function invocation mechanism works as follows.
Once the X-compiler meets the function invocation, it calls the \texttt{XHookManager}, which tries to match the function signature (in the case of program in C language -- only the function name) across all signatures it stores.
If the signature matches, the hook manager intercepts the function call and interprets the hook action instead of invoking the function directly.
The hook manager enables only invocation hooks that are compliant with the language of the input program.
All invocation hooks implement the interface \texttt{XInvocationHook}.
The result of an invocation hook interception is the \texttt{XInvocationHookAction}, a delayed operation implemented on the top of lambda functions of Java.
The hook action is invoked with actual arguments and returns an arbitrary \texttt{XEntity} as the result of invocation.

@@

Once the graph is unrolled, it can be augmented by data-flow edges.
As it was discussed in Section~\ref{ch:impl:model:xgraph}, the data-flow edges can represent either \rf{}- or \co{}-relation.
The \rf{}-edges join each write event to all read events that access the same location; the \co{}-edges join write events to the same location.
%TODO: check if this is true %Currently, \porthos[2] does not yet construct the \xgraph[DF] component of the full \xgraph{}, instead, it uses the function `\texttt{dartagnan.wmm.Domain.encode}' of \porthos[1] to encode data-flow relations and derived relations of the \xgraph[CF].

### 2018-05-30 5_eval.tex
Add example on cfg in cfg to eval. Add two siks to summary.

The unrolling algorithm used by \porthos[1] (right-hand side picture) unrolls \textit{all} loops $k$ times (where $k$ is the unrolling bound), and the unrolling algorithm of \porthos[2] unrolls loops so that not more than $k$ events are executed.
As it is illustrated by the picture, the new algorithm produces a better set of program executions (for example, the unrolled graph of \porthos[1] does not contain executions of the inner loops more than $k=2$ times, which makes the old unrolling algorithm not complete).
As the new unrolling algorithm is based on the DFS algorithm, it discovers \textit{all} possible paths, therefore the result graph contains \textit{all} possible executions and thus the program analysis performed on this graph can be complete up to bound~$k$.

@@

@@

If verifying this litmus test by \porthos[2] in the state reachability mode, the test passes for TSO memory model and fails for SC model.

>>>>

The unrolling algorithm used by \porthos[1] (right-hand side picture) unrolls \textit{all} loops $k$ times (where $k$ is the unrolling bound), and the unrolling algorithm of \porthos[2] unrolls loops so that not more than $k$ events are executed.
As it is illustrated by the picture, the new algorithm produces a better set of program executions (for example, the unrolled graph of \porthos[1] does not contain executions of the inner loops more than $k=2$ times in a raw, which makes the old unrolling algorithm not complete).
As the new unrolling algorithm is based on the DFS algorithm, it discovers \textit{all} possible paths, therefore the result graph contains \textit{all} possible executions and thus the program analysis performed on this graph can be complete up to bound~$k$.

@@

Current section demonstrates some new features of \porthos[2], which is hard or impossible to implement on the top of its predecessor \porthos[1] (see detailed discussion in Chapter~\ref{ch:impl}).

\subsection{Interpretation of a code with an arbitrary control-flow}

The following example in Figure~\ref{ex:cfg-arbitrary} illustrates the interpretation of the program that contains \textit{continue}, \textit{break} and two \texttt{goto} instructions (both forward and backward), that can produce an arbitrary control-flow graph.
As an addition, the example illustrates the interpretation of complex expressions that involve shared variables (such as the condition of the \texttt{while}-loop in the function \texttt{thread\_0}).
Note that the \texttt{entry event} of the loop is not necessarily the guard computation event.
In the case when a computation event involves shared variables, all of them need to be copied to a register before the computation event is emitted.
The first event that performs such a copy becomes an entry event of the \texttt{while}-loop, which the loop back edge and all \texttt{continue}-jumps point to.

%Note also that if the \texttt{backward} \texttt{goto}-edges (to the already processed event) can be set up at the moment of emitting the jump event, the \texttt{forward} \texttt{goto}-edges can be set up later on

\begin{figure}[!h]
\begin{lstlisting}
{
  int x = 1, *y;
}

void thread_0(int &x, int &y) {
  L0: x = 0;
  int r;
  while (x * (5 + 4 / 2) % 3 == 1) {
    if (x != 0) {
      goto L0; //backward jump
    }
    if (y > 6) {
      continue;
    }
    else if (++y > 7) {
      r = r + 10;
      break;
    }
    else {
      goto L1; //forward jump
    }
    r = 11;
  }
  y = x + 1;
  L1: x = r;
}

void thread_1() {
  while (true) {
    if (x > 7)
      break;
  }
  y = x;
}

exists (y == x + 1 && thread_0:r > 21)

\end{lstlisting}
\caption{Example of interpretation of a code with an arbitrary control-flow}
\label{ex:cfg-arbitrary}
\end{figure}

The four flow-graphs for the code in Figure~\ref{ex:cfg-arbitrary} are shown in Figure~\ref{ex:cfg-arbitrary:pic}.
There are two small linear flow-graphs for \textit{prelude} (litmus-specific variables initialisation and shared variables declaration) and \textit{postlude} (assertion) definitions.
As the initialisation statement assigns value only to one shared variable, its flow-graph has only a single event (although variable declarations change the state of the interpreter while compilation, they do not produce events).
The postlude has shared variables involved into the assertion, therefore they need to be copied into local registers beforehand.
Note how the unconditional jump instructions \texttt{goto}, \texttt{continue} and \texttt{break} are compiled in the event-flow graph for processes \texttt{thread\_0} and \texttt{thread\_1}.

\begin{figure}[!h]
\includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/cfg-arbitrary/collage.jpg}
\caption{Control-flow components of the event-flow graphs for the code in Figure~\ref{ex:cfg-arbitrary}}
\label{ex:cfg-arbitrary:pic}
\end{figure}

\subsection{Extensible compiler mapping}

@@

When verifying this litmus test by \porthos[2] in the state reachability mode, the test passes for TSO memory model and fails for SC model.

### 2018-05-30 90_summary.tex
Add example on cfg in cfg to eval. Add two siks to summary.

@@

\begin{itemize}[leftmargin=\parindent]
\item One of the major limitation of \porthos[2] as a software verification tool is its sensitivity to the \textit{combinatorial explosion} of the state space.
%that performs complete analysis
As it was shown in Section~\ref{ch:eval:perf}, the number of events of the unrolled program grow rapidly as the user increases the unrolling bound.
One possible way to reduce the number of the program states might be applying some traditional techniques that target the state explosion problem (such as concrete execution as a part of concolic execution~\cite{majumdar2007hybrid} before the unrolling stage).
However, this must be done carefully and with taking into account the analysing weak memory model, because otherwise it can lead to the loss of states and thus to incorrect analysis results.
Nonetheless, the small-size litmus test-like programs (containing hundreds of events after the unrolling) remain to be handleable by \porthos[2] within reasonable time.
% cannot be applied to our problem \textit{before} the weak memory model is considered, 
%One possible enhancement, that could treat but not cure this flaw, could be an extra analysis stage carried before the unrolling, that analyses

@@

\item \textit{Extending the knowledge base} of domain-specific functions to model synchronisation primitives can be considered as the main future research direction.
Thus, to be able to process most Linux kernel litmus tests, \porthos[2] needs to know the semantics of the barrier and memory operation functions that are specific for the Linux kernel in order to be able to compile them into the \xgraph{} and later encode them into the SMT-formula.
Due to modular architecture of \porthos[2], the extension of the knowledge base can be done by modifying solely the invocation hooking mechanism.
Note that the flip side of the flexibility of invocation hooks is their complexity: being written in Java, in addition they require from the user some knowledge of general architecture of the tool, the interface methods provided by the interpreter, the class hierarchy of the \xgraph{} elements, etc.

\item Secondly, the wide range of existing litmus tests may require \porthos[2] to \textit{extend the support for input languages}.
The first candidates for being supported are the LISA language (Litmus Instruction Set Architecture)~\cite{alglave2016syntax} and assembly languages of most common architectures (x86, POWER, Alpha, etc.).
Note that the programs in low-level languages can be easily compiled to the \xgraph{} representation by existing compiler architecture since low-level assembly-like languages can be considered as the subset of the C language, that restricts the set of non-linear control-flow instructions to the conditional and unconditional jumps (which are supported by the current \xgraph{} compiler of \porthos[2]).
%Note that adding support for low-level languages requires adding the new \xgraph{} compiler that will compile the low-level syntax tree (with non-conditional jumps as the only )

@@

\item One might want to compare the performance of \porthos[2] in cases of usage the different SMT-solvers.
Due to the \zformula{} abstraction layer, new SMT-solvers may be easily added (the general way to support multiple SMT-solvers is to convert the \zformula{} to an SMT-LIB formula~\cite{smt-lib}, that can be passed as input to the SMT-solver run as an external process).

>>>>

%TODO: written a generic hardware-agnostic extensible non-optimising compiler

@@

\begin{itemize}[leftmargin=\parindent]
\item One of the major limitation of \porthos[2] as a software verification tool is its sensitivity to the \textit{combinatorial explosion} of the state space.
%that performs complete analysis
As it was shown in Section~\ref{ch:eval:perf}, the number of events of the unrolled program grow rapidly as the user increases the unrolling bound.
One possible way to reduce the number of the program states might be applying some traditional techniques that target the state explosion problem (such as concrete execution as a part of \textit{concolic execution}~\cite{majumdar2007hybrid} before the unrolling stage).
However, this must be done carefully and with taking into account the analysing weak memory model, because otherwise it can lead to the loss of states and thus to incorrect analysis results.
Nonetheless, the small-size litmus test-like programs (containing hundreds of events after the unrolling) remain to be handleable by \porthos[2] within reasonable time.
% cannot be applied to our problem \textit{before} the weak memory model is considered, 
%One possible enhancement, that could treat but not cure this flaw, could be an extra analysis stage carried before the unrolling, that analyses

@@

\item For justifying the correctness of the verification that bases on the result of the input program unrolling, one might want to be aware whether an execution in the unrolled event-flow graph has run the loop a whole number or it was interrupted on non-last event of the loop.
This can be modelled with two kinds of sink events (completed and uncompleted) of the event-flow graph as it was discussed in Sections~\ref{ch:enc:bmc:cf} and~\ref{ch:impl:proc:x-unroll}.

\item \textit{Extending the knowledge base} of domain-specific functions to model synchronisation primitives (the compiler mapping) can be considered as the main future research direction.
Thus, to be able to process most Linux kernel litmus tests, \porthos[2] needs to know the semantics of the barrier and memory operation functions that are specific for the Linux kernel in order to be able to compile them into the \xgraph{} and later encode them into the SMT-formula.
Due to modular architecture of \porthos[2], the extension of the knowledge base can be done by modifying solely the invocation hooking mechanism.
Note that the flip side of the flexibility of invocation hooks is their complexity: being written in Java, in addition they require from the user some knowledge of general architecture of the tool, the interface methods provided by the interpreter, the class hierarchy of the \xgraph{} elements, etc.

\item The wide range of existing litmus tests may require \porthos[2] to \textit{support new input languages}.
The first candidates for being supported are the LISA language (Litmus Instruction Set Architecture)~\cite{alglave2016syntax} and assembly languages of most common architectures (x86, POWER, Alpha, etc.).
Note that the programs in low-level languages can be easily compiled to the \xgraph{} representation by existing compiler architecture since low-level assembly-like languages can be considered as the subset of the C language, that restricts the set of non-linear control-flow instructions to the conditional and unconditional jumps (which are supported by the current \xgraph{} compiler of \porthos[2]).
%Note that adding support for low-level languages requires adding the new \xgraph{} compiler that will compile the low-level syntax tree (with non-conditional jumps as the only )

@@

\item One might want to compare the performance of \porthos[2] in cases of usage the different SMT-solvers.
For that, the \zformula{} abstraction layer will be useful as new SMT-solvers can be easily added (the general way to support multiple SMT-solvers is to convert the \zformula{} to an SMT-LIB formula~\cite{smt-lib}, that can be passed as input to the SMT-solver run as an external process).
